\texorpdfstring{\ZpL}{ZpL}: a p-adic precision package

### 2018-05-07 ZpL/ZpL.tex
Adding references to Kedlaya and Lauder

When computing with real and $p$-adic fields, exact results are usually impossible,
since most elements have infinite decimal or $p$-adic expansions.
Working with these fields thus requires an analysis of how precision evolves
through the sequence of steps involved in carrying out a computation.
In this paper, we describe a package for computing with $p$-adic rings and fields \cite{trac:23505},
based on a series of papers by the same authors
\cite{caruso-roe-vaccon:14a,caruso-roe-vaccon:15,caruso-roe-vaccon:16,caruso-roe-vaccon:17}.
The core of the package is a method for tracking precision using $p$-adic lattices which
can yield dramatically more precise results, at the cost of increased runtime and memory usage.

>>>>

When computing with real and $p$-adic fields, exact results are usually impossible,
since most elements have infinite decimal or $p$-adic expansions.
Working with these fields thus requires an analysis of how precision evolves
through the sequence of steps involved in carrying out a computation.
Such analysis can be carried out automatically by the software, or via theorems specific
to a particular application \cite{kedlaya:01a, lauder:04a}.
In this paper, we describe a package for computing with $p$-adic rings and fields \cite{trac:23505},
based on a series of papers by the same authors
\cite{caruso-roe-vaccon:14a,caruso-roe-vaccon:15,caruso-roe-vaccon:16,caruso-roe-vaccon:17}.
The core of the package is a method for tracking precision using $p$-adic lattices which
can yield dramatically more precise results than traditional methods, at the cost of increased runtime and memory usage.
